Using the internal language of toposes in algebraic geometry

### 2015-11-02 abstract-ihes2015.tex
typo

  Furthermore, modal operators can be used to model phrases such as ``on a
  dense open subset it holds that`` or ``on an open neighbourhood of a given
  point it holds that``. These operators define certain subtoposes; a
  generalization of the double-negation translation is useful in order to
  understand the internal universe of those subtoposes from the internal point
  of view of the ambient topos.

>>>>

  Furthermore, modal operators can be used to model phrases such as ``on a
  dense open subset it holds that'' or ``on an open neighbourhood of a given
  point it holds that''. These operators define certain subtoposes; a
  generalization of the double-negation translation is useful in order to
  understand the internal universe of those subtoposes from the internal point
  of view of the ambient topos.
